---
title: "IndividualFits"
output: html_document
---

```{css, echo=FALSE}
    body .main-container {
      max-width: 1280px !important;
      width: 1280px !important;
    }
    body {
      max-width: 1280px !important;
    }
```

```{r setup, , echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
library("RColorBrewer")
library("ggplot2")
library("cowplot")
library(stringr)

source("preprocess_data.R")
source("FitUVSDT.R")

models <- c("GaussianEVSDT","GaussianUVSDT","GumbelEVSDT","ExGaussNormEVSDT")
experiment <- "SB2021_e2"

load_files <- function(path,pattern) {

  files <- dir(path, pattern = pattern,full.names = TRUE,recursive = FALSE)
  # search for test data (dataTEST) file in all subdirectories (recursive) of path
  tables <- lapply(files, readRDS)
  do.call(bind_rows, tables)
  # collate all of them into 1 dataframe
}

fits <- load_files("Fits2/","fit")
fullsubj <-  bind_rows(readRDS("SB2021_individualpredictions.rds"),
                      readRDS("SB2021_individualpredictions_ExGaussNorm.rds") %>%
                        filter(!pred=="observed"))


bestfit <- fits %>% filter(exp == experiment) %>% 
  filter(model %in% models) %>% 
  mutate(objective = ifelse(objective < 0, objective * -1, objective)) %>%
  mutate(AIC = 2 * npar + 2 * objective) %>%
  group_by(model,id,condition) %>%
  arrange(objective) %>%
  dplyr::slice(1) %>% 
  mutate(condid = paste0(id,"_",condition))


allfits <- bestfit %>%
  filter(model %in% models) %>%
  group_by(exp,condid) %>%
  mutate(delAIC = AIC - min(AIC))


winning <- allfits %>%
  filter(delAIC == 0)


GumbelWin <- winning %>% filter(model == "GumbelEVSDT" & delAIC == 0) %>% .$condid
EVSDTWin <- winning %>% filter(model == "GaussianEVSDT" & delAIC == 0) %>% .$condid
UVSDTWin <- winning %>% filter(model == "GaussianUVSDT" & delAIC == 0) %>%
  relocate(sigo, .after = muo) %>% .$condid
ExGaussWin <- winning %>% filter(model == "ExGaussNormEVSDT" & delAIC == 0) %>% .$condid

alls <- fullsubj %>% 
  group_by(exp,condid,model,oldnew) %>%
  mutate(responseprop = freq/sum(freq))

allresiduals <- NULL
for(subjid in unique(alls$condid)){

      datonly <- alls %>% filter(model == "Data") %>% 
      ungroup() %>% filter(condid == subjid)
    
  
    for (modelname in models) {

      modelsprop <- alls %>% filter(model == modelname) %>%
    
        filter(condid == subjid) %>%
        bind_cols(datprop = datonly$responseprop,
                  datfreq = datonly$freq) %>%
        mutate(residuals = responseprop - datprop)
      
      allresiduals <- allresiduals %>% bind_rows(modelsprop)
    
  }
}

allresiduals <- allresiduals %>% 
  mutate(confidence = factor(confidence,levels = c(1:6))) %>% 
  mutate(model = factor(model,levels = c(models),labels = c("EVSDT","UVSDT","Gumbel","ExGaussNorm")))
  

UVSDTpreds <- fullsubj %>%
  select(exp,condid,id,condition,model,confidence,oldnew,zroc,roc,freq) %>%
  pivot_wider(names_from = oldnew, values_from = c(roc,zroc,freq)) %>%
  mutate(whowins = case_when(condid %in% GumbelWin ~ "Gumbel",
                             condid %in% EVSDTWin ~ "EVSDT",
                             condid %in% UVSDTWin  ~ "UVSDT",
                             condid %in% ExGaussWin ~ "ExGaussNorm",
                             TRUE ~ "Else")) %>%
  mutate(model = factor(model,levels = c(models,"Data"),labels = c("EVSDT","UVSDT","Gumbel","ExGaussNorm","Data"))) %>%
  mutate(whowins = factor(whowins,levels = c("EVSDT","UVSDT","Gumbel","ExGaussNorm")))


Datonly <- UVSDTpreds %>% filter(model == "Data")

DatonlyLong <- Datonly  %>% select(exp,pred,condid,id,condition,model,confidence,freq_New,freq_Old,whowins) %>%
  pivot_longer(!c(exp,condid,id,condition,model,confidence,whowins,pred),names_to="oldnew",values_to="freq") %>%
  mutate(confidence = factor(confidence, levels = c(1:6))) %>%
  mutate(oldnew = factor(oldnew,levels = c("freq_New","freq_Old"),labels = c("New","Old")))


partable <- bestfit %>% 
  select(model,exp,condid,id,condition,objective,muo,sigo,betao,c1,dc1,dc2,dc3,dc4) %>%
  pivot_longer(!c(exp,condid,id,condition,model),names_to="estimates",values_to="value") %>%
  mutate(estimates = factor(estimates, levels = rev(c("objective",
                                                "muo","sigo","betao","c1","dc1","dc2","dc3","dc4")))) %>% 
   mutate(model = factor(model,levels = c(models),labels = c("EVSDT","UVSDT","Gumbel","ExGaussNorm"))) 

UVSDTpredsLong <- UVSDTpreds  %>% select(exp,condid,id,condition,model,pred,confidence,freq_New,freq_Old,whowins) %>%
  pivot_longer(!c(exp,condid,id,condition,model,pred,confidence,whowins),names_to="oldnew",values_to="freq") %>%
  mutate(confidence = factor(confidence, levels = c(1:6))) %>%
  mutate(oldnew = factor(oldnew,levels = c("freq_New","freq_Old"),labels = c("New","Old")))




# A: High Strength, high EV
# B: High Strength, low EV
# C: Low strength, high EV
# D: Low Strength, low EV

labelconditions <- tibble(condition = c("A","B","C","D"),
                          conditionlabel = c("high strength, high variability",
                                             "high strength, low variability",
                                             "low strength, high variability",
                                             "low strength, low variability"))


```


```{r, echo=FALSE,message=FALSE,warning=FALSE}


allparticipants <- unique(fullsubj$condid)

plots_list = list()

for (i in seq_along(allparticipants)){

  subjid <- allparticipants[[i]]

ind <- allfits %>% filter(condid == subjid) %>%
  bind_rows(tibble(delAIC = 0,model="A",condid = subjid)) %>%
  mutate(model = factor(model,levels = c("A",models),labels = c("Winning","EVSDT","UVSDT","Gumbel","ExGaussNorm")))

maxDelta <- max(allfits %>% filter(condid == subjid) %>% .$delAIC) + 5



maxlim <- max(0.045,abs(allresiduals %>% filter(condid == subjid) %>% .$residuals)) + 0.005

resids <- ggplot(allresiduals %>% filter(condid == subjid),
       aes(x = confidence,y = residuals,color=model,fill=model,group=model,shape=model)) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(limits = c(-maxlim,maxlim),name = "Residuals of response proportions")+
  scale_color_manual(name = "Fitted Model",values = c("#56B4E9","#E69F00", "#009E73","#CC79A7")) +
  scale_fill_manual(name = "Fitted Model",values = c("#56B4E9","#E69F00", "#009E73","#CC79A7")) +
  scale_shape_manual(name = "Fitted Model", values = c(22,21,24,23))+
  
  geom_line(size = 1, position = position_dodge(width = .6))+
  geom_point(size = 3, position = position_dodge(width = .6),color="black")+
    facet_grid(oldnew~.) +
  theme(axis.title.x = element_blank(),
        axis.text.y = element_text(size=12),
        #axis.ticks = element_blank(),
        #legend.position = "none",
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = "transparent",colour="black"),
        strip.placement = "outside",
        #legend.position = "bottom",
        strip.background = element_rect(fill = "transparent",
                                        colour="transparent"),
        strip.text = element_text(size = 12))




AICplot <- ggplot(ind,
       aes(x = model, y = delAIC,fill=model)) +
 geom_hline(yintercept = 1, linetype="dashed")+
  geom_hline(yintercept = 2, linetype="dashed")+
  geom_hline(yintercept = 0)+
  geom_bar(stat = "identity") +
  scale_fill_manual(name = "Fitted Model",values = c("#000000","#56B4E9","#E69F00","#009E73","#CC79A7")) +
  coord_cartesian(ylim = c(0,15))+
  scale_y_continuous(limits = c(0,maxDelta),name = expression(paste(Delta, " AIC")),breaks=c(0,1,2,5,10,15)) +
 
 scale_x_discrete()+
  geom_text(data = ind, aes(x = 1,y = 5,angle=90,
                            label = paste(unique(ind %>% filter(delAIC == 0) %>% .$model %>% .[[1]]))),
            size=5)+
  theme(axis.title.x = element_blank(),
    axis.text.y = element_text(size=12),
    axis.text.x = element_text(angle=45,hjust=1),
    #axis.ticks = element_blank(),
    legend.position = "none",
    panel.background = element_rect(fill = "white"),
    panel.border = element_rect(fill = "transparent",colour="black"),
    strip.placement = "outside",
    #legend.position = "none",
    strip.background = element_rect(fill = "transparent",
                                    colour="transparent"),
    strip.text = element_text(size = 12))




minscale <- min(Datonly %>% filter(condid == subjid) %>% .$zroc_New,
                Datonly %>% filter(condid == subjid) %>% .$zroc_Old,
                UVSDTpreds %>% filter(condid == subjid) %>% .$zroc_New,
                UVSDTpreds %>% filter(condid == subjid) %>% .$zroc_Old,na.rm=T) - 0.2

maxscale <- max(Datonly %>%  filter(condid == subjid) %>% .$zroc_New,
                Datonly %>% filter(condid == subjid) %>% .$zroc_Old,
                UVSDTpreds %>%  filter(condid == subjid) %>% .$zroc_New,
                UVSDTpreds %>%  filter(condid == subjid) %>% .$zroc_Old,na.rm=T) + 0.2

zroc <- ggplot(Datonly %>%  filter(condid == subjid),
       aes(x = zroc_New,y = zroc_Old)) +
  geom_point(data = UVSDTpreds %>% filter(model != "Data") %>% filter(condid == subjid),
             aes(x = zroc_New,y = zroc_Old,color=model,shape=model),size=2)+
  geom_abline(intercept=0,slope=1)+
  geom_smooth(data = UVSDTpreds %>% filter(model != "Data") %>%
               filter(condid == subjid),
              aes(x = zroc_New,y = zroc_Old,color=model),size=1,
              method="lm",formula = y ~ poly(x, 2), se = FALSE,fullrange=T)+
  scale_color_manual(name = "Fitted Model",values = c("#56B4E9","#E69F00", "#009E73","#CC79A7")) +
  #scale_fill_manual(name = "Winning Model",values = c("#56B4E9","#E69F00", "#009E73"))+
  scale_shape_manual(name = "Fitted Model",values = c(16,15,17,18))+
  geom_point(data = Datonly  %>% filter(condid == subjid),aes(x = zroc_New,y = zroc_Old), color= "black",size=3,shape=15)+
  # geom_point(data = Datonly  %>% filter(condition == cond) %>% filter(id == subjid),aes(x = 2,y = -2,fill = whowins,shape = whowins),
  #            size=4)+
  scale_x_continuous(name = "z(fa)",limits = c(minscale,maxscale)) +
  scale_y_continuous(name = "z(hit)",limits = c(minscale,maxscale)) +

  theme(aspect.ratio=1,
        axis.text = element_text(size=12),
        #axis.ticks = element_blank(),
        legend.position = c(0.7,0.25),
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = "transparent",colour="black"),
        strip.placement = "outside",
        #legend.position = "none",
        legend.box.background = element_rect(fill="transparent"),
        strip.background = element_rect(fill = "transparent",
                                        colour="transparent"),
        strip.text = element_text(size = 12))



confrating <- ggplot(data = DatonlyLong %>% filter(condid == subjid),
       aes(y = freq,x = confidence)) +
  geom_bar(stat="identity",color="black",fill="lightgrey") +
  geom_point(data = UVSDTpredsLong %>% filter(model != "Data") %>% filter(condid == subjid),
             aes(y = freq,x=confidence,fill=model,shape=model),
             size=2,position=position_dodge(width=0.8))+
  #geom_text(aes(label=round(freq)))+
  scale_fill_manual(name = "Fitted Model",values = c("#56B4E9","#E69F00", "#009E73","#CC79A7"))+
  scale_shape_manual(name = "Fitted Model",values = c(22,21,24,23))+
  # scico::scale_fill_scico(palette = "bilbao")+
  # scale_fill_gradient2(limits = c(0, 60),
  #                      low = "white",high = "red") +
  #
  #
  #geom_text(aes(label = round(delAIC)),size = 3.5) +
  # scale_fill_manual(values = c("#ffff00","#000000","#ffffff","#ff0000","#00ff00","#0000ff"),
  #                   labels = c("no responses","responses",NA,"Gumbel > 10","GaussianEVSDT > 10",
  #                              "GaussianUVSDT > 10"))+
  scale_y_continuous(limits = c(0,60)) +
  #scale_y_discrete(labels = c("New","Old"))+
  facet_grid(oldnew~.)+

  theme(axis.title = element_blank(),
        axis.text.y = element_text(size=12),
        #axis.ticks = element_blank(),
        legend.position = "none",
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = "transparent",colour="black"),
        strip.placement = "outside",
        #legend.position = "none",
        strip.background = element_rect(fill = "transparent",
                                        colour="transparent"),
        strip.text = element_text(size = 12))


parametertable <-  ggplot(data = partable %>% filter(condid == subjid),
         aes(y = model,x = estimates)) +
  geom_tile(fill = "white",color="white") +
  geom_text(aes(label=round(value,2)))+
  scale_x_discrete(position = "bottom",labels = rev(c("-LL","con.",expression(mu[o]),expression(sigma[o]),expression(lambda[o]),"c1",
                                               "dc1","dc2","dc3","dc4")))+
    scale_y_discrete(position = "right",labels = c("EVSDT","UVSDT","Gumbel","ExGaussNorm"))+
    coord_flip()+
  theme(axis.title = element_blank(),
        axis.text.y = element_text(size=12),
        axis.text.x = element_text(size=10),
        axis.ticks = element_blank(),
        panel.background = element_rect(fill = "white"),
        panel.border = element_rect(fill = "transparent",colour="black"),
        strip.placement = "outside",
        #legend.position = "none",
        strip.background = element_rect(fill = "transparent",
                                        colour="transparent"),
        strip.text = element_text(size = 12))

CondLabel <- labelconditions %>% filter(condition == str_sub(subjid,start=-1)) %>% .$conditionlabel


title <- ggdraw() + 
  draw_label(
    paste0(str_sub(subjid,1,nchar(subjid)-2),", condition ",str_sub(subjid,start=-1), " (", CondLabel,")"),
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )


plots <- plot_grid(AICplot,parametertable,zroc,confrating,resids,nrow=1,labels="AUTO",
                   rel_widths=c(0.4,0.5,0.6,0.4,0.7))

plots_list[[i]] <- plot_grid(title,plots,rel_heights = c(0.1,1),nrow=2)


}



```
# SB2021_e2

2 memory strength (low, high) x 2 encoding variability (low, high) within-subjects, between-blocks recognition memory design.

* A: High Strength, high EV
* B: High Strength, low EV
* C: Low strength, high EV
* D: Low Strength, low EV

Individual-level plots of data, model fits and predictions of equal-variance Gaussian SDT (EVSDT, 6 parameters), unequal-variance Gaussian SDT (UVSDT, 7 parameters) and Gumbel SDT (Gumbel, 6 paraneters). 

Split by condition, and winning-model (in tabs).

Plots:

* **A**: Comparison by Delta AIC, cut-off at 15
* **B** : Parameter estimates
* **C**: zROC of data and model predictions (lines fitted by y = x^2). Note: scales vary by plot
* **D**: frequency of responses observed (bars) and predicted (symbols)
* **E**: residuals of predicted proportion of responses to observed data (+ means model predicts higher proportion of responses) in all response categories. Note: y-scale varies by plot



## Condition A {.tabset} 

High memory strength, High encoding variability


```{r, echo=FALSE,message=FALSE,warning=FALSE}

# find participants in condition A, B, C, D where EVSDTwin, UVSDTwin, Gumbelwin

criticalEVSDT_index <- match(EVSDTWin[str_detect(EVSDTWin, "_A")],allparticipants)
criticalUVSDT_index <- match(UVSDTWin[str_detect(UVSDTWin, "_A")],allparticipants)
criticalGumbel_index <- match(GumbelWin[str_detect(GumbelWin, "_A")],allparticipants)
criticalExGauss_index <- match(ExGaussWin[str_detect(ExGaussWin, "_A")],allparticipants)

```

### EVSDT wins (N = ``r length(criticalEVSDT_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalEVSDT_index){

  
  cat("  \n")

  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```

### UVSDT wins (N = ``r length(criticalUVSDT_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalUVSDT_index){

  cat("  \n")
  
  plot(plots_list[[i]])
  
  cat("  \n")

}
```

### Gumbel wins (N = ``r length(criticalGumbel_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalGumbel_index){

  cat("  \n")
  
  plot(plots_list[[i]])
  
  cat("  \n")

}
```

### ExGauss-Norm wins (N = ``r length(criticalExGauss_index)``)

```{r echo=FALSE, fig.height=4, fig.width=20, message=FALSE, warning=FALSE, results="asis"}

for(i in criticalExGauss_index){
  
  cat("  \n")

  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```

## Condition B {.tabset} 

High memory strength, Low encoding variability


```{r, echo=FALSE,message=FALSE,warning=FALSE}

# find participants in condition A, B, C, D where EVSDTwin, UVSDTwin, Gumbelwin

criticalEVSDT_index <- match(EVSDTWin[str_detect(EVSDTWin, "_B")],allparticipants)
criticalUVSDT_index <- match(UVSDTWin[str_detect(UVSDTWin, "_B")],allparticipants)
criticalGumbel_index <- match(GumbelWin[str_detect(GumbelWin, "_B")],allparticipants)
criticalExGauss_index <- match(ExGaussWin[str_detect(ExGaussWin, "_B")],allparticipants)

```

### EVSDT wins (N = ``r length(criticalEVSDT_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalEVSDT_index){

  cat("  \n")
  
  plot(plots_list[[i]])
  
  cat("  \n")

}
```

### UVSDT wins (N = ``r length(criticalUVSDT_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}


for(i in criticalUVSDT_index){

  cat("  \n")
  
  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```

### Gumbel wins (N = ``r length(criticalGumbel_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalGumbel_index){
  
  cat("  \n")

  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```

### ExGauss-Norm wins (N = ``r length(criticalExGauss_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalExGauss_index){
  
  cat("  \n")

  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```

## Condition C {.tabset} 

Low memory strength, high encoding variability


```{r, echo=FALSE,message=FALSE,warning=FALSE}

# find participants in condition A, B, C, D where EVSDTwin, UVSDTwin, Gumbelwin

criticalEVSDT_index <- match(EVSDTWin[str_detect(EVSDTWin, "_C")],allparticipants)
criticalUVSDT_index <- match(UVSDTWin[str_detect(UVSDTWin, "_C")],allparticipants)
criticalGumbel_index <- match(GumbelWin[str_detect(GumbelWin, "_C")],allparticipants)
criticalExGauss_index <- match(ExGaussWin[str_detect(ExGaussWin, "_C")],allparticipants)

```

### EVSDT wins (N = ``r length(criticalEVSDT_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalEVSDT_index){

  cat("  \n")
  
  plot(plots_list[[i]])
  
  cat("  \n")

}
```

### UVSDT wins (N = ``r length(criticalUVSDT_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}


for(i in criticalUVSDT_index){

  cat("  \n")
  
  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```

### Gumbel wins (N = ``r length(criticalGumbel_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalGumbel_index){
  
  cat("  \n")

  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```

### ExGauss-Norm wins (N = ``r length(criticalExGauss_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalExGauss_index){
  
  cat("  \n")

  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```

## Condition D {.tabset} 
 
Low memory strength, low encoding variability


```{r, echo=FALSE,message=FALSE,warning=FALSE}

# find participants in condition A, B, C, D where EVSDTwin, UVSDTwin, Gumbelwin

criticalEVSDT_index <- match(EVSDTWin[str_detect(EVSDTWin, "_D")],allparticipants)
criticalUVSDT_index <- match(UVSDTWin[str_detect(UVSDTWin, "_D")],allparticipants)
criticalGumbel_index <- match(GumbelWin[str_detect(GumbelWin, "_D")],allparticipants)
criticalExGauss_index <- match(ExGaussWin[str_detect(ExGaussWin, "_D")],allparticipants)

```

### EVSDT wins (N = ``r length(criticalEVSDT_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalEVSDT_index){

  cat("  \n")
  
  plot(plots_list[[i]])
  
  cat("  \n")

}
```

### UVSDT wins (N = ``r length(criticalUVSDT_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}


for(i in criticalUVSDT_index){

  cat("  \n")
  
  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```

### Gumbel wins (N = ``r length(criticalGumbel_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalGumbel_index){
  
  cat("  \n")

  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```

### ExGauss-Norm wins (N = ``r length(criticalExGauss_index)``)

```{r, echo=FALSE,message=FALSE,warning=FALSE,results="asis",fig.width = 20,fig.height=4}

for(i in criticalExGauss_index){
  
  cat("  \n")

  plot(plots_list[[i]])
  
  cat("  \n")
  
}
```